R Notebook

### 2022-04-10 Code/Simulation.Rmd
changed gev fit function, captions for hists

```{r}
# Load packages
library(xtable)
library(dgof)
library(tidyverse)
library(KSgeneral)
library(copula)
library(evd)
source('tspb.R')
```

@@

# Generate results
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

@@

# Generate histograms plot
hist_copula <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_copula

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 100
b1 <- 0.5
b2 <- 0.3

@@

# Generate histograms plot
hist_copula_ar2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 100
ma <- 0.5

@@

# Generate histograms plot
hist_copula_ma1 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 100
ar <- 0.5
ma <- 0.3

@@

# Generate histograms plot
hist_copula_arma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

# Set variables
n <- 100
rho <- 0.7
counter <- 0
nrep <- 1000
B <- 100
shape <- 3
scale <- 1

@@

    # Get observed stat
    fit <- fgev(x, std.err = FALSE)
    loc <- fit$estimate[1]
    scale <- fit$estimate[2]
    shape <- fit$estimate[3]

@@

        fit.b <- fgev(x.b, std.err = FALSE)
        loc.b <- fit.b$estimate[1]
        scale.b <- fit.b$estimate[2]
        shape.b <- fit.b$estimate[3]

@@

  # Summarize parameters
  fit <- fgev(x)
  loc <- fit$estimate[1]
  scale <- fit$estimate[2]
  shape <- fit$estimate[3]

@@

    fit.b <- fgev(x.b)
    loc.b <- fit.b$estimate[1]
    scale.b <- fit.b$estimate[2]
    shape.b <- fit.b$estimate[3]

@@

  fit <- fgev(x)
  loc <- fit$estimate[1]
  scale <- fit$estimate[2]
  shape <- fit$estimate[3]

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 100
loc <- 0
shape <- 1
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- suppressWarnings(replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = 1, scale = 1, copula = normalCopula, rho = rho), B = B)))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))

# P-vals from naively using fitted parameters
pvals_naive <- suppressWarnings(replicate(nrep, test_super_naive_gamma(genData(n, qgev, shape = 1, scale = 1, copula = normalCopula, rho = rho))$p.value))

@@

>>>>

```{r}
# Load packages
library(xtable)
library(dgof)
library(tidyverse)
library(KSgeneral)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1000
B <- 100

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

@@

# Generate histograms plot
hist_copula <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s", ar))
hist_copula

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
b1 <- 0.5
b2 <- 0.3

@@

# Generate histograms plot
hist_copula_ar2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = (%s, %s)", b1, b2))

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ma <- 0.5

@@

# Generate histograms plot
hist_copula_ma1 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("MA = %s", ma))

@@

# Set variables
n <- 100
counter <- 0
nrep <- 1000
B <- 1000
ar <- 0.5
ma <- 0.3

@@

# Generate histograms plot
hist_copula_arma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s, MA = %s", ar, ma))

@@

# Set variables
n <- 100
rho <- 0.7
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

@@

    # Get observed stat
    fit <- gev.fit(x, show = FALSE)
    loc <- fit$mle[1]
    scale <- fit$mle[2]
    shape <- fit$mle[3]

@@

        fit.b <- gev.fit(x.b, show = FALSE)
        loc.b <- fit.b$mle[1]
        scale.b <- fit.b$mle[2]
        shape.b <- fit.b$mle[3]

@@

  # Summarize parameters
  fit <- gev.fit(x, show = FALSE)
  loc <- fit$mle[1]
  scale <- fit$mle[2]
  shape <- fit$mle[3]

@@

    fit.b <- gev.fit(x.b, show = FALSE)
    loc.b <- fit.b$mle[1]
    scale.b <- fit.b$mle[2]
    shape.b <- fit.b$mle[3]

@@

  fit <- gev.fit(x, show = FALSE)
  loc <- fit$mle[1]
  scale <- fit$mle[2]
  shape <- fit$mle[3]

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 100
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_gev(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho), B = B))
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- suppressWarnings(replicate(nrep, test_parametric_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value))

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, qgev, loc = 0, shape = shape, scale = 1, copula = normalCopula, rho = rho))$p.value)

@@

```{r}
ptm <- proc.time()

# Set variables
n <- 100
ar <- 0.5
counter <- 0
nrep <- 1
B <- 100

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), "pnorm", B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_super_naive(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n))$p.value)

# Generate histograms plot
hist_copula_only <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("AR = %s", ar))
hist_copula_only

# Save the histogram figure
ggsave(filename = "hist_copula_only.pdf", plot = hist_copula_only, path = "../Manuscript", height = 2.1, width = 6)
```
